PANCHANGE_data_preprocessing

### 2020-08-10 PANCHANGE_data_preprocessing2020-07-15.Rmd
renamed the covid symptoms variable

```{r how many people expereinced all symptoms}
dat.glad.coping <- dat.glad.coping %>%
  mutate(
    people_with_symptoms =
      if_else(
          !is.na(respiratory.anosmia_binary) &
          !is.na(respiratory.pcough_binary) &
          !is.na(respiratory.fatigue_binary) &
          !is.na(respiratory.skipped_meals_binary),
        1,
        0
       )
  )

table(dat.glad.coping$people_with_symptoms)
```

>>>>

```{r how many people expereinced all symptoms}
dat.glad.coping <- dat.glad.coping %>%
  mutate(
    covid_symptoms =
      if_else(
          !is.na(respiratory.anosmia_binary) &
          !is.na(respiratory.pcough_binary) &
          !is.na(respiratory.fatigue_binary) &
          !is.na(respiratory.skipped_meals_binary),
        1,
        0
       )
  )

dat.glad.coping %>%
  freq(covid_symptoms, cumul = F)
```
